Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-15 docs/google-research-awards-latam/main.tex
polish igor text (still some PL-related inconsistencies)

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
demands of the community and these changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions. Automated test generation can help reduce the
cost of testing, but the lack of executable specifications is an
important obstacle. In particular, it is an obstable to find functional errors.

@@

The workflow described in Section~\ref{sec:design} is currently functional. This section shows preliminary
results obtained with our infrastructure providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}. 
\Igor{
  The \CodeIn{valueOf} is an object property that returns the primitive value
  of the specific object\cite{valueof} and in the original version of this code,
  the \CodeIn{valueOf} function returns an empty string.
  The modified code returns a string representation of an embedded null terminator
  value. 
  The unary plus ``\CodeIn{+a}" is equivalent to \CodeIn{String.ToNumber(a.valueOf())} 
  that converts a variable to a number, but if the value cannot be converted, 
  the return should be the value NaN (Not a Number) \cite{unary-plus}.
  As such, the engines evaluate that unary plus as a NaN value 
  at the assertion expression; hence test execution is expected to fail. 
  Chakra, however, is able to parse the string as a number zero, making the test to pass.
}
\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

@@

%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL
%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly

>>>>

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
demands of the community and these changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions. Automated test generation can help reduce the
cost of testing, but the lack of executable specifications is an
important obstacle. In particular, it is an obstacle to find functional errors.

@@

The workflow described in Section~\ref{sec:design} is currently
functional. This section shows preliminary results obtained with our
infrastructure providing some evidence that finding bugs in JS runtime
engines is promising. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of a
month. For example, bug \# 6 was manifested by the JS code \CodeIn{var
  a = \{valueOf:~function()\{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}}.  The object property \CodeIn{valueOf} stores a
function that returns a primitive value identifying the target
object~\cite{valueof}. That function returns an empty string in the
original version of this code. The modified version of the code
returns a string representation of a null character (called
\CodeIn{NUL} in ascii).
The unary plus expression ``\CodeIn{+a}", appearing in the assertion,
is equivalent to the expression \CodeIn{String.ToNumber(a.valueOf())}
that converts a string to a number, but if the string cannot be
converted, the expression should evaluate to NaN (Not a Number)
\cite{unary-plus}. For this case, all engines but Chakra evaluate the unary
plus to NaN as expected, as the null character cannot be converted. As result, the test fails as
expected. Chakra, in contrast, incorrectly converts the string to zero, making the test to pass.

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[20]{tr}[0pt]{0.5\textwidth}
  \vspace{-2ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

@@

%%  LocalWords:  d'Amorim oes Jornalista Fernandes JS Patra Pradel
%%  LocalWords:  fuzzer runtime WebAssembly's codebases Radamsa JSC
%%  LocalWords:  fuzzers linters JavaScriptCore SpiderMonkey AFL NUL
%%  LocalWords:  HonggFuzz jsfunfuzz Grammarinator WebAssembly ascii
%%  LocalWords:  valueOf unary NaN Chakra cccccc Url JavascriptCore
%%  LocalWords:  cgi tmp
